|

### 2023-01-30 paper.Rmd
autogit

```{r airfoil-finalFitness, echo=FALSE, fig.cap="Fitness after 30 Generations - Airfoil (1HL)", out.width="80%"}
knitr::include_graphics("./img/airfoil_1hl_150hn_fullRun_30gens/final_fit_boxplot.png")
```

@@

Since pre-trained thus far did not demonstrate significant benefits for DAE-GP, this section describes two alternative pre-training strategies, Second Generation Pre-Training and  Grow-Initialized Pre-Training, that are also tested for the airfoil dataset.

@@

<!-- describe total runtime, including/excluding pre-training time -->

>>>>

```{r airfoil-finalFitness, echo=FALSE, fig.cap="Fitness after 30 Generations - Airfoil (1HL)", out.width="80%"}
knitr::include_graphics("./img/airfoil_1hl_150hn_30gens/final_fit_boxplot.png")
```

@@

Since pre-training thus far did not demonstrate significant benefits for the quality of solutions found by DAE-GP, this section describes two alternative pre-training strategies, Second Generation Pre-Training and  Grow-Initialized Pre-Training, that are also tested for the airfoil dataset.

@@

One important argument for using pre-training DAE-GP is that it might be a potential way to reduce the overall run-time of the algorithm by reducing the training time of each generations DAE-LSTM model. Especially in the context of optimization problems where solutions have to be found numerous times in a time efficient manner (e.g. Vehicle Routing in the Domain of Logistic Services), one major advantage of pre-training is that a pre-trained model can be re-used to optimize many instances of an optimization problem.

### 2023-01-30 paper.tex
autogit

@@

{\centering \includegraphics[width=0.8\linewidth]{./img/airfoil_1hl_maxIndSize_fullRun_30gens/mean_median_fitness_byGens}

@@

{\centering \includegraphics[width=0.8\linewidth]{./img/airfoil_1hl_maxIndSize_fullRun_30gens/final_fit_boxplot}

@@

\hypertarget{alternative-pre-training-strategies}{%
\subsection{Alternative Pre-Training Strategies}\label{alternative-pre-training-strategies}}

Since pre-trained thus far did not demonstrate significant benefits for DAE-GP, this section describes two alternative pre-training strategies, Second Generation Pre-Training and Grow-Initialized Pre-Training, that are also tested for the airfoil dataset.

>>>>

\hypertarget{reduced-number-of-hidden-layers}{%
\subsubsection{Reduced Number of Hidden Layers}\label{reduced-number-of-hidden-layers}}

@@

{\centering \includegraphics[width=0.8\linewidth]{./img/airfoil_1hl_150hn_30gens/mean_median_fitness_byGens}

@@

{\centering \includegraphics[width=0.8\linewidth]{./img/airfoil_1hl_150hn_30gens/final_fit_boxplot}

@@

\hypertarget{alternative-pre-training-strategies}{%
\subsubsection{Alternative Pre-Training Strategies}\label{alternative-pre-training-strategies}}

Since pre-training thus far did not demonstrate significant benefits for the quality of solutions found by DAE-GP, this section describes two alternative pre-training strategies, Second Generation Pre-Training and Grow-Initialized Pre-Training, that are also tested for the airfoil dataset.
